


```{r}
#| label: setup
#| warning: false
library(data.table)
library(targeter)
library(gt)

# print(params$object)
object <- qs::qread(params$object)
#print(object) 
```



## Analysis


```{r}
stats <- setDT(object$profiles[[1]]$target_stats)
Ntot <- stats[, sum(count)]
if (object$target_type == "binary"){
  stats[, reference_level := ifelse(as.character(value) == as.character(object$target_reference_level), "*", "")]
}
```



:::: {.columns}

**Parameters**

::: {.column}
- Data used: `r object$dataname`
- Descrition of data: `r ifelse(!is.null(object$description_data), object$description_data, "no description provided.")`
- Analysis performed the: `r object$date`
- Target: `r paste(object$target, ifelse(!is.null(object$description_target), object$description_target, ""))` [`r object$target_type`]
- Number of variables: `r length(object$profiles)`
- Analyzed population contains: `r Ntot` records.
:::

::: {.column}

**Target Statistics**


```{r}
gt(stats)
```

:::
::::


```{r}
#| output: asis
i <- 1
cat("\n## ",names(object$profiles)[i],"")


```

