---
title:  "`r object$analysis`"
author: "targeter package"
date: "`r object$date`"
output:
  html_document:
    toc: true
    toc_float:
      toc_collapsed: true
  word_document:
    toc: true
  pdf_document:
    toc: true
classoption: landscape
header-includes:
  - \usepackage{array}
  - \usepackage{booktabs}
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(targeter)
library(data.table)
library(ggplot2)
library(DT)

# source('/hackdata/share/code/R/packages/targeter/R/plot.R', local=TRUE)
# source('/hackdata/share/code/R/packages/targeter/R/fullplot.R', local=TRUE)

```



```{r, eval=FALSE}
metadata <- attr(object, "metadata")
```

\newpage

## Introduction

This report contains a snapshot of the variable of interest **«`r label(object$target,metadata)` ». 

This subpopulation is characterized by  performing bivariate analyses, crossing the variable of interest (target) with  potential explanatory variables. Only most relevant (highest discriminative power) may be retained.

Report contains:

*   A summary overview table with selected retained criteria with some available information such as one statistic called information value (IV) that provides an idea of the explanatory power of the criteria.
*   Detailed analyses per criteria with graphics that highlight the reation between one of the candidate criteria and the _target_.


### Summary table interpretation

Criteria are sorted by decreasing importance order, which one is determined by the IV. 

For this report, we selected a maximum of  `r ntop` potential criteria.



\newpage

## Population description

```{r, ,results='asis'}
 if(!is.null(object$description_data)){
   cat(object$description_data[[1]])}else{cat("No information on data have been provided during the analysis.")}

stats <- setDT(object$profiles[[1]]$target_stats)
Ntot <-stats[, sum(count)]
cat("\n Analyzed population contains ",Ntot," records.")
```

## Target description


```{r,results='asis'}


if(!is.null(object$description_target)) {
  cat(object$description_target[[1]])} else{
     cat("No description of the target has been provided during the analysis.")}

cat("  \n Target statistics:")
# knitr::kable(stats, format=format_tables)
if (format_tables=="word"){
   flextable::set_flextable_defaults(font.size = 11)
  flextable::qflextable(stats)
  
} else if (format_tables=="html") {
  suppressWarnings(kableExtra::kable_styling(knitr::kable(stats, format=format_tables)))
} else if (format_tables=="latex"){
    knitr::kable(stats, format= "latex", booktabs = TRUE)
    }


```

\newpage

## Summary view


```{r summarytable}
##filter df columns; remove varname (we have rownames) keep only: index.max.index, index.max.level, index.max.count,
df2 <- as.data.frame(summary_object)



df2 <- df2[,-2] # remove targetname column
colnames(df2)[1] <- c("variable")
df2$IV <- round(df2$IV,6)

if ('F' %in% colnames(df2)){
  df2$F <- round(df2$F,0)
  df2$pval <- formatC(df2$pval)
  
}
# [the relevant section](#test)

if (!is.null(metadata)){
 df2 <- cbind(data.frame(Label=sapply(df2$variable,label, metadata=metadata),stringsAsFactors = FALSE),df2)
 rownames(df2) <- NULL
}
if (format_tables=="latex"){
  knitr::kable(df2, format= "latex", booktabs = TRUE)
  
} else  if (format_tables=="html"){
  df2$variable <- paste0("<a href='#var-",tolower(df2$variable),"'>",df2$variable,"</a>")
  # kableExtra::kable_styling(knitr::kable(df2, format=format_tables))
DT::datatable(df2, rownames = FALSE, filter="top", 
              selection="none", autoHideNavigation = TRUE, 
              escape = -ifelse(is.null(metadata),1,2),
              options=list(pageLength=25))
}  else  if (format_tables=="word") {
# word 
  flextable::qflextable(df2)
}

```



\newpage


## Variables


```{r, results='asis', echo=FALSE, fig.height=8, fig.width=9, fig.align='center'}
# varnames <- sapply(object$profiles, function(x) x$varname)
varnames <- summary_object$varname

for (i in seq_along(varnames)){
  
ivar <- varnames[i]
ivar_label = label(ivar, metadata = metadata)
iprofile <- object$profiles[[ivar]]
# https://stackoverflow.com/questions/39281266/use-internal-links-in-rmarkdown-html-output
# explicit link: you give a custom name to a header ## Test {#test} and later refer to it with a link syntax: see [the relevant section](#test).
cat("\n\n\\newpage\n\n")
if (format_tables=="html"){
  
  cat(paste0("<div id='var-",tolower(ivar),"'>\n\n## ",label(ivar, metadata=metadata), ifelse(ivar_label!=ivar, paste0(" (",ivar,")"),""),"\n</div>"))
  
} else {
cat("\n\n### ",label(ivar, metadata=metadata),"\n")
  
}

cat("\n__IV:", round(iprofile$IV,6),"__\n\n")
print(fullplot(iprofile))

cat('\\pagebreak')
}
```

