---
title: "Introduction to the targeter Package"
author: "welovedatascience"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    highlight: tango
vignette: >
  %\VignetteIndexEntry{Introduction to targeter}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  warning = FALSE,
  message = FALSE, 
  fig.width = 9, 
  fig.height = 6
)
```

## Introduction to targeter

The `targeter` package is designed for profiling and analyzing the relationship between a target variable (which you want to explain or predict) and potential explanatory variables (features). It provides tools for:

* Automatic variable type detection and classification
* Binning of numeric variables into interpretable categories
* Calculating statistics that highlight relationships with the target
* Computing Weight of Evidence (WOE) and Information Value (IV) for binary targets
* Visualizing these relationships through various plots

`targeter` is particularly useful for:

* Exploratory data analysis prior to modeling
* Understanding which variables are most predictive of a target
* Investigating how different values of variables affect the target
* Creating insightful visualizations of variable relationships

This vignette demonstrates the basic functionality of `targeter` using the included `adult` dataset and exploring factors related to income levels.

## Getting Started

Let's start by loading the package and the adult dataset:

```{r load}
# Load required packages
library(targeter)
library(ggplot2)

# Load the adult dataset that comes with the package
data(adult)

# Take a look at the dataset
str(adult)
```

## Overview of the adult dataset

The `adult` dataset contains census information with various demographic indicators and a binary target variable `ABOVE50K` that indicates whether a person's income exceeds $50,000 per year.

```{r data_overview}
# Basic summary of the dataset
dim(adult)
summary(adult$ABOVE50K)
table(adult$ABOVE50K)
```

The target variable shows that approximately `r round(sum(adult$ABOVE50K)/length(adult$ABOVE50K)*100, 1)`% of individuals in the dataset have income above $50K.

## Basic Usage: Profiling the Target Variable

The core function of the package is `targeter()`, which creates a comprehensive 
profile of the relationship between the target variable 
and explanatory variables.

Minimum call is to invoke `targeter()` with the dataset and the target variable
as following:

```{r basic_profile}
# Run a basic profile of the ABOVE50K variable
tar <- targeter(
  data = adult,
  target = "ABOVE50K"
)

# Look at the structure of the resulting object
class(tar)
names(tar)
```

The `targeter` function has created a comprehensive profile of our target variable. Let's explore some of the key insights we can extract.

## Exploring Results: Summary Information

We can use the `summary` function to get an overview of the most important variables:

```{r summary}
# Get a summary of the targeter profiles object
tar_summary <- summary(tar)
head(tar_summary, 10)
```

The summary table shows variables sorted by their Information Value (IV), a measure of their predictive power for the target variable. Higher IV values indicate stronger predictive ability.

## Visualizing Relationships

The `targeter` package provides several visualization functions to explore the relationships between variables and the target:

### 1. Basic variable plots

```{r basic_plot}
# Plot the relationship between EDUCATION and income
plot(tar$profiles$EDUCATION)
```

### 2. Full variable profile plots

```{r fullplot}
# Generate a comprehensive plot for one of the top variables
fullplot(tar$profiles$RELATIONSHIP)
```

## Weight of Evidence (WOE) and Information Value (IV)

For binary targets like our income variable, the Weight of Evidence (WOE) shows how different categories of a variable influence the target:

```{r woe}
# Look at WOE values for a variable
head(tar$profiles$OCCUPATION$woe)

# Display Information Value for key variables
vars_with_iv <- sapply(tar$profiles, function(x) x$IV)
sorted_iv <- sort(vars_with_iv, decreasing = TRUE)
head(sorted_iv, 10)
```

WOE values tell us:
* Positive values: that category is associated with higher probability of the target
* Negative values: that category is associated with lower probability of the target
* The magnitude indicates the strength of the relationship

## Customizing the Analysis

`targeter` offers many customization options:

```{r custom_analysis}
# Run a more customized analysis
custom_tar <- targeter(
  data = adult,
  target = "ABOVE50K",
  # Only select a few variables of interest
  select_vars = c("AGE", "EDUCATION", "OCCUPATION", "HOURSPERWEEK", "SEX"),
  # Customize the binning of numeric variables
  nbins = 6,
  description_data = "US Census data with demographic and income information",
  description_target = "Binary indicator of income above $50k per year",
  binning_method = "quantile",
  # Control how results are displayed
  order_label = "count"
)

# Look at the numeric variable binning
plot(custom_tar$profiles$AGE)
```

## Using Batch Processing for Larger Datasets

For larger datasets with many variables, you can use batch processing:

```{r batch_processing}
# Process variables in batches of 5
batch_tar <- targeter(
  data = adult,
  target = "ABOVE50K",
  by_nvars = 2,
  verbose = TRUE
)
```

## Creating a Report

The `targeter` package also allows you to create comprehensive reports:

```{r report, eval=FALSE}
# Generate a report (not run in the vignette to keep it short)
report(tar, output_file = "adult_income_profile.html")
```

## Summary

The `targeter` package provides powerful tools for exploratory data analysis and understanding variable relationships. In this vignette, we've covered:

1. Creating a basic profile of a target variable
2. Exploring the most important variables through summary statistics
3. Visualizing relationships between variables and the target
4. Understanding Weight of Evidence and Information Value
5. Customizing the analysis for specific needs

These basic operations should get you started with u the package. For more advanced functionality, consult the package documentation and additional vignettes.

```{r session_info}
# Session information for reproducibility
sessionInfo()
```